---
title: "p8105_hw1_mff2137.Rmd"
author: "Mohammad"
date: "2022-09-23"
output: github_document
---

```{r, message = FALSE, error = FALSE}
library(tidyverse)
```

This is a markdown document!

# Problem 1
 
## Data
 
I will use this code to load the `penguins` dataset: 
 
```{r chunk_data}
data("penguins", package = "palmerpenguins")
```

## Description

The `penguins` dataset has `r ncol(penguins)` columns and `r nrow(penguins)` rows. 
Here's a summary of the the important variables and values in this dataset showing 
the names and sums for species and island variables, the type, sum, and number of 
NA's for sex variable, and the minimum, 1st quantile, median, mean, 3rd quantile, 
maximum, and number of NA's respectively for the body mass variable: species: `r summary(penguins$species)`, island: `r summary(penguins$island)`, body mass: 
`r summary(penguins$body_mass_g)` , and sex: `r summary(penguins$sex)`.

## Mean

I can take the mean of the flipper length. The mean is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)`.

## Plot 

I can make a scatterplot of the flipper length and bill length by species. 

```{r chunk_scatterplot, echo = FALSE, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

# Problem 2

## New Dataframe

I can create a data frame using this **code chunk**

```{r chunk_dataframe}
set.seed(20)
hw_df <- tibble(
    samp = rnorm(10, mean = 0, sd = 1),
    vec_log = samp > 0,
    vec_char = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
    vec_factor = factor(c("y", "n", "m", "y", "m", "n", "n", "y", "y", "m"), 
                        levels = c("y", "n", "m"))
)
```

## Means

I can try to take the means of the variables in this data frame. The mean of the 
random sample is `r mean(pull(hw_df, samp))`. The mean of the logical vector is 
`r mean(pull(hw_df, vec_log))`. The mean of the character vector is `r mean(pull(hw_df, vec_char))`.
The mean of the factor vector is `r mean(pull(hw_df, vec_factor))`. We notice that
the means for the character vector and factor vector returns as `NA` because their
arguments are not numeric or logical. 

## Converting variables

I can convert the logical, character, and factor variables to numeric using the following code:

```{r, eval = FALSE}
hw_df <- tibble(
    samp = rnorm(10, mean = 0, sd = 1),
    vec_log = as.numeric(samp > 0),
    vec_char = as.numeric(c("1", "2", "3", "4", "4", "6", "7", "8", "9", "10")),
    vec_factor = as.numeric(factor(c("y", "n", "m", "y", "m", "n", "n", "y", "y", "m"), 
                                   levels = c("y", "n", "m")))
)
```

Now we notice that we can get the means for all variables in the dataset. The mean 
of the random sample is `r round(mean(pull(hw_df, samp)), 2)`. The mean of the logical
vector is `r round(mean(pull(hw_df, vec_log)), 2)`. The mean of the character vector is
`r round(mean(pull(hw_df, vec_char)), 2)`. The mean of the factor vector is 
`r round(mean(pull(hw_df, vec_factor)), 2)`. This is because value for all variables
are now converted to numeric.

